A Documentary History of \\ the Nock Combinator Calculus

### 2025-07-07 mss.tex
Add whynock

Perhaps better put, Nock is a family of combinator calculi that sequentially converge on an ``optimal'' expressiveness for certain design desiderata.  This includes an economy of expression (thus several macro opcodes) and consideration of how a higher-level language would invoke stored procedural expressions.  Furthermore an opcode exists which produces and then ignores a computation, intended to signal to a runtime layer that a side effect may be desired by the caller.

>>>>

Perhaps better put, Nock is a family of combinator calculi that sequentially converge on an ``optimal'' expressiveness for certain design desiderata.  This includes an economy of expression (thus several macro opcodes) and consideration of how a higher-level language would invoke stored procedural expressions.  Furthermore an opcode exists which produces and then ignores a computation, intended to signal to a runtime layer that a side effect may be desired by the caller.\footnote{An able if dated document from January 2010, \href{https://github.com/cgyarvin/urbit/blob/1bc9086a3fd62594e8bd631744cb9bf804f6a43b/Spec/urbit/5-whynock.txt}{\texttt{5-whynock.txt}}, further expounds desiderata for Nock in the context of Urbit as operating function.}
